Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-10 draft.tex
change 'n' to 't' throughout section 2

The payoff functions and all parameters, including probabilities in the war lottery, are common knowledge for all players, and actions are immediately observed by all players at the time they occur. There are an infinite number of periods $n=1,2,\ldots$, with play proceeding until an absorbing state is reached.

Future payoffs are discounted with a common parameter $\de$, where 1/$\de$ is each player's discount rate and $0\leq\de\leq1$.\footnote{All of the results that follow go through essentially unchanged in the general case where the players potentially discount at different rates. This simplifying assumption is made solely to highlight the essential mechanisms of the model.} Therefore payoffs for the entire game for player $i\in \{s, g, p, c\} $ can be expressed by the discounted stream of payments $\Sigma_{n=1}^{\infty} U_{in} \de^{n-1}$.

@@

\item $p$ chooses a level of resource expenditure $R_{pn}\in \mathbb{R}^+$ in period $n$ and invests it to alter the payoffs of players $s$ and/or $g$.

\item $c$ chooses a level of resource expenditure $R_{cn}\in \mathbb{R}^+$ in period $n$ and invests it to alter the payoffs of players $s$ and/or $g$.

@@

\noindent Stage game payoffs for players $s$ and $g$ in period $n$, gross of investments by players $p$ and $c$, are:
\vspace{2pt}
\begin{center}
\begin{tabular}{|  c| c | c | c |} 
\hline
  $g\downarrow$,     $ s\rightarrow$  & Fight & Status Quo &Cede \\ \hline
	Fight & $\Omega_n$ &$\Omega_n$&$W_{gn}, L_{sn}$ \\ \hline
	Status Quo& $\Omega_n$& $Q_{gn}, Q_{sn}$ &$W_{gn}, L_{sn}$ \\ \hline
	Cede&$L_{gn}, W_{sn}$& $L_{gn}, W_{sn}$ &$Q_{gn}, Q_{sn}$ \\ \hline
 \multicolumn{4}{c} {Figure 2: Stage Game Payoffs}\\ 
\end{tabular}
\end{center}
\vspace{2.5pt}

@@

For probabilities $p_1$ of outright victory and $1-p_1$ of loss, player $i \in \{s, g\}$ in period $n$ with a fixed cost of war $\zeta_i$ faces war lottery $ \omega_{in} \equiv (p_1 (W_{in}-\zeta_i), \left(1-p_1\right)( L_{in}-\zeta_i))$. $\Omega_n \equiv (\omega_{gn}, \omega_{sn}).$\footnote{Baseline costs of war are fixed ($\zeta_i$) but additional costs of war based on war's result are captured in $W_i$ and $L_i$.} Players are assumed to approach war lotteries as expected values.

If both $s$ and $g$ play Status Quo, then the status quo persists. The status quo payoffs for the secessionists are modeled as steadily declining due to the costs of non-recognition discussed in the introduction. As the economy in the secessionist region deteriorates, so does the standard of living for the secessionists. Therefore, the payoffs from the status quo, in the absence of other actions, are given by $q_{s,n+1} = Q_{s,n} - \mu$. Lower case letters denote beginning-of-period quantities net of investments by outside actors, while upper case letters denote end-of-period quantities gross of such investments. Other payoffs remain unchanged from period to period; they can only be altered by the investments of players $p$ or $c$, e.g. $L_{s,n} = l_{s,n} + R_{p,n} + R_{c,n}$ and $l_{s,n+1} = L_{s,n}$, likewise for player $g$ and for the payoffs from winning for both players and the status quo for player $g$. %who can expend resources ($R$) to increase a payoff at the rate $\gamma$.  For example, if $p$ expends resources to aid the secessionists, the payoff $Q_s$ becomes $Q_s+\gamma R_p$ in the round that the resources are expended.

@@

At the start of each period, the patron, $p$, and player $c$ may invest resources to affect the payoffs of $s$ and $g$ in the stage game. For example, if $p$ expends resources $R_{pn}$ to increase the secessionists status quo payoffs, the beginning-of-period payoff $q_{sn}$ becomes end-of-period payoff $Q_{sn} = q_{sn} + R_{pn}$. We can write analogous expressions for $q_{gn}, \ l_{sn},\ l_{gn},\ w_{sn}$, and $w_{sn}$, and the international community can also make investments to increase whichever of these payoffs they like. $B_{pn}$ denotes the total that the patron can devote to interceding in the conflict; we assume that player $c$, which is often a large coalition of states, does not have a binding budget constraint.

@@

Player $p$'s payoffs in period $n$ are $U_{pn}= -\alpha X+\lambda Y -R_{pn}$, while the payoffs for player $c$ are $U_{cn}= \beta X-\nu Y -R_{cn}$, with both payoffs denoted in currency units. Taking $\alpha, \ \beta, \lambda,$ and $\nu$ to be positive, these payoffs represent the idea that the patron opposes reunification while player $c$ prefers it, and that the patron prefers recognized independence while player $c$ is averse to the creation of new states.

>>>>

The payoff functions and all parameters, including probabilities in the war lottery, are common knowledge for all players, and actions are immediately observed by all players at the time they occur. There are an infinite number of periods $t=1,2,\ldots$, with play proceeding until an absorbing state is reached.

Future payoffs are discounted with a common parameter $\de$, where 1/$\de$ is each player's discount rate and $0\leq\de\leq1$.\footnote{All of the results that follow go through essentially unchanged in the general case where the players potentially discount at different rates. This simplifying assumption is made solely to highlight the essential mechanisms of the model.} Therefore payoffs for the entire game for player $i\in \{s, g, p, c\} $ can be expressed by the discounted stream of payments $\Sigma_{t=1}^{\infty} U_{it} \de^{t-1}$.

@@

\item $p$ chooses a level of resource expenditure $R_{pt}\in \mathbb{R}^+$ in period $t$ and invests it to alter the payoffs of players $s$ and/or $g$.

\item $c$ chooses a level of resource expenditure $R_{ct}\in \mathbb{R}^+$ in period $t$ and invests it to alter the payoffs of players $s$ and/or $g$.

@@

\noindent Stage game payoffs for players $s$ and $g$ in period $n$, gross of investments by players $p$ and $c$, are:
\vspace{2pt}
\begin{center}
\begin{tabular}{|  c| c | c | c |} 
\hline
  $g\downarrow$,     $ s\rightarrow$  & Fight & Status Quo &Cede \\ \hline
	Fight & $\Omega_t$ &$\Omega_t$&$W_{gt}, L_{st}$ \\ \hline
	Status Quo& $\Omega_t$& $Q_{gt}, Q_{st}$ &$W_{gt}, L_{st}$ \\ \hline
	Cede&$L_{gt}, W_{st}$& $L_{gt}, W_{st}$ &$Q_{gt}, Q_{st}$ \\ \hline
 \multicolumn{4}{c} {Figure 2: Stage Game Payoffs}\\ 
\end{tabular}
\end{center}
\vspace{2.5pt}

@@

For probabilities $p_1$ of outright victory and $1-p_1$ of loss, player $i \in \{s, g\}$ in period $t$ with a fixed cost of war $\zeta_i$ faces war lottery $\omega_{it} \equiv (p_1 (W_{it}-\zeta_i), \left(1-p_1\right)( L_{it}-\zeta_i))$. $\Omega_t \equiv (\omega_{gt}, \omega_{st}).$\footnote{Baseline costs of war are fixed ($\zeta_i$) but additional costs of war based on war's result are captured in $W_i$ and $L_i$.} Players are assumed to approach war lotteries as expected values.

If both $s$ and $g$ play Status Quo, then the status quo persists. The status quo payoffs for the secessionists are modeled as steadily declining due to the costs of non-recognition discussed in the introduction. As the economy in the secessionist region deteriorates, so does the standard of living for the secessionists. Therefore, the payoffs from the status quo, in the absence of other actions, are given by $q_{s,t+1} = Q_{s,t} - \mu$. Lower case letters denote beginning-of-period quantities net of investments by outside actors, while upper case letters denote end-of-period quantities gross of such investments. Other payoffs remain unchanged from period to period; they can only be altered by the investments of players $p$ or $c$, e.g. $L_{s,t} = l_{s,t} + R_{p,t} + R_{c,t}$ and $l_{s,t+1} = L_{s,t}$, likewise for player $g$ and for the payoffs from winning for both players and the status quo for player $g$. %who can expend resources ($R$) to increase a payoff at the rate $\gamma$.  For example, if $p$ expends resources to aid the secessionists, the payoff $Q_s$ becomes $Q_s+\gamma R_p$ in the round that the resources are expended.

@@

At the start of each period, the patron, $p$, and player $c$ may invest resources to affect the payoffs of $s$ and $g$ in the stage game. For example, if $p$ expends resources $R_{pt}$ to increase the secessionists status quo payoffs, the beginning-of-period payoff $q_{st}$ becomes end-of-period payoff $Q_{st} = q_{st} + R_{pt}$. We can write analogous expressions for $q_{gt}, \ l_{st},\ l_{gt},\ w_{st}$, and $w_{st}$, and the international community can also make investments to increase whichever of these payoffs they like. $B_{pt}$ denotes the total that the patron can devote to interceding in the conflict; we assume that player $c$, which is often a large coalition of states, does not have a binding budget constraint.

@@

Player $p$'s payoffs in period $t$ are $U_{pt}= -\alpha X+\lambda Y -R_{pt}$, while the payoffs for player $c$ are $U_{ct}= \beta X-\nu Y -R_{ct}$, with both payoffs denoted in currency units. Taking $\alpha, \ \beta, \lambda,$ and $\nu$ to be positive, these payoffs represent the idea that the patron opposes reunification while player $c$ prefers it, and that the patron prefers recognized independence while player $c$ is averse to the creation of new states.
